R-LIME\@: Rectangular Constraints and Optimization for Local Interpretable Model-agnostic Explanation Methods

### 2024-07-09 paper.tex
modify details on paper

\subsection*{Summary of revisions}
We would like to appriciate all the reviewers for their clear and insightful
comments.
We improved our paper from the original version according to their comments.
The major revision points are listed as follows:
\begin{enumerate}
  \item We added an overview of other existing methods to \cref{sec:related-work}.
  \item We added discussion about parameter selection in \cref{sec:param}.
  \item We conducted comparisons between Anchor and R-LIME to \cref{sec:related-work}.
\end{enumerate}
Please see below for a point-by-point response to each reviewer's comments.

@@

\input{src/fig-examples}
\subsubsection{Experimental Results}
The results of the experiment are shown in \cref{fig:A,fig:B}.
The values assigned to each feature name represent the contribution
(weight of the linear classifier)
to the output of the black-box classifier,
normalized such that the absolute sum is 1.
The figures display the 5 features with the highest absolute contribution.

@@

\vspace{-5pt}
\subsubsection{Experimental Results}
The results are presented in \cref{fig:box-plot},
showing the distribution of the local accuracy of the linear classifiers
learned by LIME and R-LIME\@.
R-LIME achieved higher accuracy compared to LIME for all values of $\tau$.
This suggests that the linear classifiers learned by LIME and R-LIME
differ significantly,
and R-LIME learns a high-accuracy linear classifier
adapted to the optimized rectangular region.
Additionally, as $\tau$ increases,
the variability in the accuracy of LIME widens.
This indicates that the linear classifiers learned by LIME may not function
effectively as approximation models depending on how the region is selected.

\subsection{\hl{Quantitative Evaluation: Anchor vs. R-LIME}}\label{sec:exp-anchor}
\subsubsection{\hl{Experimental Setup}}
\hl{
  To demonstrate that R-LIME explanations are more general than Anchor,
  we conducted a comparison of the coverage of explanations
  between Anchor and R-LIME\@.
  Under the same settings as in
}\cref{sec:exp-setting},
\hl{
  we generated Anchor and R-LIME explanations
  for 100 instances from the test data of the recidivism dataset,
  under the values of $\tau=0.70,0.80,0.90$.
}

>>>>

\subsection*{Summary of revisions}
We would like to appriciate all the reviewers for their clear and insightful
comments.
We improved our paper from the original version according to their comments.
The major revision points are listed as follows:
\begin{enumerate}
  \item We added an overview of other existing methods to \cref{sec:related-work}.
  \item We added discussion about parameter selection in \cref{sec:param}.
  \item We conducted qualitative and quantitative comparisons
        between Anchor and R-LIME in \cref{sec:exp-qual,sec:exp-anchor}.
\end{enumerate}
Please see below for a point-by-point response to each reviewer's comments.

@@

  {%
    \def\scale{0.315}
    \def\dir{exp1/ver1/examples/output}
    \def\imgwidth{0.3\textwidth}
    \def\hspacebase{\hspace{-1.5em}}
    \def\vspacebase{\vspace{0.5em}}
    \def\vspacebeforecaption{\vspace{-0.4em}}
    \begin{figure}[t]
      \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \begin{subfigure}[t]{\textwidth}
          \hspace{-10pt}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/lime-0012}
          \caption{LIME}\label{fig:lime-0}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0012-70}  % chktex 8
          \caption{\hl{Anchor ($\tau=0.70$)}}\label{fig:anchor-0-70}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0012-90}  % chktex 8
          \caption{\hl{Anchor ($\tau=0.90$)}}
          \vspace{1.0em}
        \end{subfigure}
      \end{subfigure}
      \hfill
      \begin{subfigure}[t]{0.45\textwidth}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-5pt}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0012-70}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.70$)}\label{fig:rlime-0-70}
          \vspacebase{}
        \end{subfigure}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-17pt}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0012-90}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}
          \vspacebase{}
        \end{subfigure}
      \end{subfigure}
      \caption[Explanation for Instance A by LIME and R-LIME]{%
        Explanation for Instance A by LIME and R-LIME\@.
      }\label{fig:A}
    \end{figure}
    \begin{figure}[t]
      \begin{subfigure}[t]{0.45\textwidth}
        \begin{subfigure}[t]{\textwidth}
          \hspace{-26.5pt}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/lime-0011}
          \caption{LIME}\label{fig:lime-1}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0011-70}  % chktex 8
          \caption{\hl{Anchor ($\tau=0.70$)}}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0011-90}  % chktex 8
          \caption{\hl{Anchor ($\tau=0.90$)}}
          \vspace{1.0em}
        \end{subfigure}
      \end{subfigure}
      \hfill
      \begin{subfigure}[t]{0.45\textwidth}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-5pt}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0011-70}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}
          \vspacebase{}
        \end{subfigure}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-20pt}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0011-90}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}\label{fig:rlime-1-90}
          \vspacebase{}
        \end{subfigure}
      \end{subfigure}
      \caption[Explanation for Instance B by LIME and R-LIME]{%
        Explanation for Instance B by LIME and R-LIME\@.
      }\label{fig:B}
    \end{figure}
  }

\subsubsection{Experimental Results}
The results of the experiment are shown in \cref{fig:A,fig:B}.
The values assigned to each feature name represent the contribution
(weight of the linear classifier)
to the output of the black-box classifier,
normalized such that the absolute sum is 1.
The figures display the 5 features with the highest absolute contribution.

@@

\subsubsection{Experimental Results}
The results are presented in \cref{fig:box-plot},
showing the distribution of the local accuracy of the linear classifiers
learned by LIME and R-LIME\@.
R-LIME achieved higher accuracy compared to LIME for all values of $\tau$.
This suggests that the linear classifiers learned by LIME and R-LIME
differ significantly,
and R-LIME learns a high-accuracy linear classifier
adapted to the optimized rectangular region.
Additionally, as $\tau$ increases,
the variability in the accuracy of LIME widens.
This indicates that the linear classifiers learned by LIME may not function
effectively as approximation models depending on how the region is selected.

\subsection{\hl{Quantitative Evaluation: Anchor vs. R-LIME}}\label{sec:exp-anchor}
\subsubsection{\hl{Experimental Setup}}
\hl{
  To demonstrate that R-LIME explanations are more general than Anchor,
  we conducted a comparison of the coverage of explanations
  between Anchor and R-LIME\@.
  Under the same settings as in
}\cref{sec:exp-setting},
\hl{
  we generated Anchor and R-LIME explanations
  for 100 instances from the test data of the recidivism dataset,
  under the values of $\tau=0.65,0.70,0.75,0.80,0.85,0.90$.
}
